%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Campus Ambassador} % Job title
    {\href{http://hasura.io}{Hasura}} % Organization
    {India} % Location
    {Jan. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing Hasura Developer Groups, Parternship with other hackathons.}
        \item {Mentorship at hackathons/other coding events, Engagement with other developer communities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Campus Ambassador} % Job title
    {\href{https://internshala.com/}{Internshala}} % Organization
    {India} % Location
    {Sep. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learn to lead from the front and develop essential skills like marketing, communication while representing Internshala in college campus. }
        \item {As an ISP I have learnt - Campaigning, Seminar, Social Media Activities, Traffic Generation, Training.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{IT Engineer and Core Developer} % Job title
	{\href{http://citabu.ac.in/}{Chartered Institute of Technology}} % Organization
	{AbuRoad, India} % Location
	{July 2016 - Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Managing college intranet (pfSense): captive portal, radius, squid etc.}
			\item {Developing ERP and software for the college digitalization. Teaching Assistance in software and hardware LAB.}
			\item {Assisting students in software and hardware LAB.}
			\item {Designing brochures, pamphlets, souvenirs for the events.}
		\end{cvitems}
	}
%---------------------------------------------------------
  \cventry
    {Engineering Intern} % Job title
    {ThinkTree - Where Ideas Breath} % Organization
    {Indore, India} % Location
    {May - July 2017 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Got to know the different philosophy of art, creativity and software.}
        \item {Worked on different aspects of media like cine graphics, outdoor advertising, website developing, branding, campaigning, corporate identity etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
