%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
%\cvsubsection{International}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
	{CITErp} % Project Title
	{Developed College Management System that includes teacher leave modules, student details, incorporating with pfsense radius database and college database.} % Description
	{\href{https://github.com/CITABU/citabu_erp}{GitHub}} % Location
	{July 2017 - Pre.} % Date(s)

%---------------------------------------------------------
  \cvhonor
	{LittleGroot} % Project Title
	{Arduino based plant monitorisation that includes water level, pH level, proximity sensor etc.} % Description
	{\href{https://github.com/vijaypurohit/little_groot}{GitHub}} % Location
	{Dec. 2017} % Date(s)
	
%---------------------------------------------------------
  \cvhonor
	{ThinkFoodie} % Project Title
	{Android Application for information on all the major culinary methods in practices all over India. Developed API and implemented progressive web app.} % Description
	{\href{https://github.com/vijaypurohit/thinkFoodie}{GitHub}} % Location
	{Oct. 2017} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
	 {BioNicAn} % Project Title
	 {Laravel Web Portal for Digitalisation of Andaman and Nicobar diversity.} % Description
	 {\href{https://github.com/vijaypurohit/Bionican}{GitHub}} % Location
	 {Mar. - Apr. 2017} % Date(s)
	 
%---------------------------------------------------------
  \cvhonor
    {\href{https://play.google.com/store/apps/details?id=org.jirawalajaintirth.jirawalajaintirth&hl=en}{JirawalaApp}} % Project Title
    {Developed API for the android application Jirawala Jain Tirth and Tirth room booking.} % Description
    {\href{https://github.com/vijaypurohit/jirawalaApp_api}{GitHub}} % Location
    {Feb. 2017} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {T\&P\_Letter} % Project Title
    {Developed web app backened to auto generate internships letter based on information provided by students for Training and Placement Cell.} % Description
    {\href{https://github.com/vijaypurohit/T-P_letterhead}{GitHub}} % Location
    {Jan. 2017} % Date(s)
    	
%---------------------------------------------------------
  \cvhonor
    {TubeBox} % Project Title
    {Laravel based youtube clone that uses open source libraries for video manipulation and social interactions. It includes both local storage as well as Amazon S3 Cloud services.} % Description
    {\href{https://github.com/vijaypurohit/tubebox}{GitHub}} % Location
    {Jan. - July 2017} % Date(s)
%---------------------------------------------------------
  \cvhonor
    {Wien2K} % Project Title
    {Provides the files needed and detailed process to install the wien2k 14.2 in Linux.} % Description
    {\href{https://github.com/vijaypurohit/wien2k}{GitHub}} % Location
    {Dec. 2016} % Date(s)

%---------------------------------------------------------
\end{cvhonors}
