%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}

\cvsubsection{Hackathons}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}
%---------------------------------------------------------
  \cvhonor
	{\href{http://change.rajasthan.gov.in/catches/index}{Challenge for Change(DoITC)}} % Project Title
	{Presentation for the solution of the hardware project Water Canal Leakage.} % Description
	{Jaipur} % Location
	{Jan. 2018} % Date(s)

%---------------------------------------------------------
  \cvhonor
	{\href{https://innovate.mygov.in/drdo-cyberchallenge/}{DRDO Cyber Challenge}} % Affiliation/role
	{Online CTF Competition. Got to know about security features and analysis tools.} % Organization/group
	{Virtual} % Location
	{Dec. 2017} % Date(s)

%---------------------------------------------------------
  \cvhonor
	{\href{http://digifest.rajasthan.gov.in/udaipurhackathon.aspx}{Rajasthan Hackathon 3.0 (Digifest)}} % Affiliation/role
	{Leader, Selected for the hardware project Plant Monitorisation.} % Organization/group
	{Udaipur} % Location
	{Dec. 2017} % Date(s)

%---------------------------------------------------------
  \cvhonor
	{\href{https://innovate.mygov.in/world-food-india-hackathon-2017/}{World Food India Hackathon} (MoFPI)} % Affiliation/role
	{Selected for the project Regional Culinary Mobile application. The only team selected from Rajasthan State. \href{https://blog.mygov.in/announcing-shortlisted-entries-for-world-food-india-hackathon-2017-final-round/}{mygov blog}} % Organization/group
	{New Delhi} % Location
	{Oct. 2017} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://event.data.gov.in/challenges/opengovdatahack-jaipur/}{OpenGovData Hackathon}} % Affiliation/role
    {Selected for the project BloodBank tracker application created using government open data.} % Organization/group
    {Jaipur} % Location
    {Oct. 2017} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://innovate.mygov.in/sih2017/}{Smart India Hackathon} (Ministry of Earth Science)} % Affiliation/role
    {Selected for the project digitalisation of Andaman \& Nicobar Islands. Portal aims to mobilize a collaborative community that will help to build high-quality map-based multimedia information on biodiversity in Andaman and Nicobar group of Islands } % Organization/group
    {Chennai} % Location
    {Apr. 2017} % Date(s)

%---------------------------------------------------------
\end{cvhonors}


\cvsubsection{College}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}
	
%---------------------------------------------------------
  \cvhonor
	{\href{https://www.facebook.com/citabuinfo/posts/1229195450520361}{Engineer's Day}}% Affiliation/role
	{Leader, Winner of the Engineer's day events like Social Engineers, Technical Skit, Humorous Video on Engineer’s Life, Technical Fault Hunter, Quiz and Project Exhibition.} % Organization/group
	{AbuRoad} % Location
	{Sep. 2017} % Date(s)
	
%---------------------------------------------------------
  \cvhonor
	{Tarunya} % Affiliation/role
	{Winner of the Photography Competition. Participated in various Technical Events.} % Organization/group
	{AbuRoad} % Location
	{Apr. 2016,17} % Date(s)
	
%---------------------------------------------------------
\end{cvhonors}